%-------------------------
% Resume in Latex
% Author : Shreyas Malhotra
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}
\linespread{1.1}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx, multicol}
\usepackage[T1]{fontenc}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{ragged2e}
\input{glyphtounicode}

\usepackage[a4paper, margin=1.25in]{geometry}

\hyphenpenalty=10000
\exhyphenpenalty=10000

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\setlength{\footskip}{4.35004pt}

% Sections formatting
\titleformat{\section}{
  \vspace{2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{2pt}]

% Ensure PDF is machine-readable
\pdfgentounicode=1

%-------------------------
% Custom commands
\renewcommand{\labelitemi}{--} % Set dash as bullet point

\newcommand{\resumeItem}[1]{
  \item[--]\small{#1} % Align bullets consistently
}

\newcommand{\resumeSubheading}[4]{
  \item \vspace{1pt}
    \begin{tabularx}{\textwidth}{Xr}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabularx} \vspace{1pt}
}

\newcommand{\resumeCertHeading}[2]{
    \item
    \begin{tabularx}{\textwidth}{Xr}
      \small#1 & #2 \\
    \end{tabularx}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[topsep=1pt, itemsep=1pt, leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize} \vspace{1pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}, topsep=2pt]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge Shreyas Malhotra} \\ \vspace{4pt}
    \small \href{tel:+916284747449}{\underline{(+91) 62847-47449}} $|$ \small \href{mailto:shreyasmalhotra2003@gmail.com}{\underline{shreyasmalhotra2003@gmail.com}} \\
    \small \href{https://linkedin.com/in/shreyas-malhotra}{\underline{linkedin.com/in/shreyas-malhotra}} $|$
    \small \href{https://github.com/shreyas-malhotra}{\underline{github.com/shreyas-malhotra}}
\end{center}

%-----------EXPERIENCE-----------

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Technical Content Engineer - Contract}{Mar 2025 -- Present}
      {\href{https://osmsec.xyz}{OsmSec}}{}
      \resumeItemListStart
        \resumeItem{Designed and built virtual labs, CTF challenges, and hands-on exercises for clients like OffSec and Parrot CTFs, focusing on real-world relevance and skill application.}
        \resumeItem{Authored clear, concise documentation for lab setups, challenges, and walkthroughs to ensure a seamless user experience.}
        \resumeItem{Continuously refined and updated existing training content to match evolving attack surfaces and industry standards.}
        \resumeItem{Worked closely with the team to brainstorm and innovate new ways to teach cybersecurity concepts.}
        \resumeItem{Conducted in-depth CVE analysis to inform and enhance the development of relevant training content.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Security Engineer - Internship}{Mar 2022 -- May 2022}
      {\href{https://fourcore.io}{FourCore Labs}}{}
      \resumeItemListStart
        \resumeItem{Analyzed global cybersecurity incidents and delivered comprehensive reports leveraging the MITRE ATT\&CK framework.}
        \resumeItem{Proactively pursued research topics to expand knowledge base and deliver valuable insights.}
      \resumeItemListEnd

    \resumeSubheading
      {Technical Community Specialist - Internship}{Mar 2022 -- Aug 2022}
      {\href{https://whizoid.com}{Whizoid Studio}}{}
      \resumeItemListStart
        \resumeItem{Coordinated and led technical workshops, CTFs, and cybersecurity seminars, emphasizing practical skill enhancement.}
        \resumeItem{Delivered technical support during live events, resolving real-time issues for seamless delivery.}
      \resumeItemListEnd

    \resumeSubheading
      {IT Support Technician - Apprenticeship}{May 2019 -- Aug 2020}
      {Logictech Computers}{}
      \resumeItemListStart
        \resumeItem{Built and maintained computer systems, resolving technical issues to ensure optimal performance.}
        \resumeItem{Performed priority data recovery tasks, retrieving critical information within strict deadlines.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lovely Professional University}{Aug 2022 -- Jul 2025}
      {BCA - Bachelor of Computer Applications, CGPA: 8.74}{}
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------

\section{Certifications}
  \resumeSubHeadingListStart
    \resumeCertHeading
      {\textbf{eJPT - Junior Penetration Tester} $|$ \emph{INE Security}}{Dec 2024 -- Dec 2027}
    \resumeCertHeading
      {\textbf{CC - Certified in Cybersecurity} $|$ \emph{ISC2}}{Jan 2023 -- Jul 2026}
    \resumeCertHeading
      {\textbf{RH124 - Red Hat System Administration I} $|$ \emph{Red Hat}}{Jul 2024}
    \resumeCertHeading
      {\textbf{RH134 - Red Hat System Administration II} $|$ \emph{Red Hat}}{Jul 2024}
  \resumeSubHeadingListEnd

%-----------ACCOMPLISHMENTS-----------

\section{Accomplishments}
\resumeItemListStart
    \resumeItem{\textbf{Achieved 1st place} in \textbf{Chakravyuh CTF 2025}, a 12-hour CTF competition hosted by the \textbf{School of CSE, Lovely Professional University}.}
    \resumeItem{\textbf{Secured 2nd place} in \textbf{Hack Quest CTF 2024}, a 24-hour CTF competition hosted by \textbf{upGrad India}.}
    \resumeItem{Placed within the \textbf{top 15 competitors} in \textbf{VulnX CTF 2024}, a 24-hour CTF competition organized by the \textbf{VULNCON Security Conference}.}
    \resumeItem{Achieved a \textbf{global top 2\% ranking} on \textbf{TryHackMe}, a practical Cyber Security training platform.}
    \resumeItem{Placed within the \textbf{top 50 competitors} in \textbf{BitGuard Cybersecurity Hackathon 2024}, a 20-day CTF competition by \textbf{Mercer|Mettl}.}
    \resumeItem{Placed \textbf{54th} in \textbf{CloudSEK CTF 2024}, a 6-hour CTF competition organized by \textbf{CloudSEK}.}
\resumeItemListEnd

\end{document}